Detecting Facial Expressions in Professional Tennis Matches

### 2017-06-30 Report06-12.Rmd
Order the bar chart type bars

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(tables)
library(xtable)
library(ggthemes)
library(EBimage)

@@

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
  ggplot(dataset, aes(x=factor(xvar), y=proportion, group = type, fill=type)) + geom_bar(stat = "identity", position = "dodge") +
    ylab("Proportion of faces matched") + xlab(factorVar)
}

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(tables)
library(xtable)
library(ggthemes)
library(EBImage)

@@

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +
    ylab("Proportion of faces matched") + xlab(factorVar)
}
